Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-13 WSSSPE3/report/wg_main_funding_spec_expert.tex
edits in RSE main section

Measures of impact and success for research programming groups, as well as for individual research software engineers, will
be required in order to make the case to the University for continued funding. Research software engineers will not be measured by publications, we hope, but by other measures. \todo{what measures?} Middle-author publications are common for RSEs. Most RSEs welcome co-authorship on papers where the PIs consider the contribution deserves it.
(these last two statements seem contradictory, not sure which message is to be used?)

@@

For more detail on the discussion, see Appendix~\ref{sec:appendix_funding_spec_expert}.

>>>>

Measures of impact and success for research programming groups, as well as for individual research software engineers, will
be required in order to make the case to the University for continued funding. Research software engineers will not be measured by publications, we hope, but by other measures. Middle-author publications are common for RSEs. Most RSEs welcome co-authorship on papers where the PIs think that the contribution deserves it.

@@

For more details on the discussion, see Appendix~\ref{sec:appendix_funding_spec_expert}.
